%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Collaboration in the development of software and data science projects } % Job title
    {TheMadFox - Colombia} % Organization
    {Remote Work} % Location
    {April 2021 - May 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
\item {Download data from API, merge it, filter it and create a end-point using Django}
\item {Extract information from html files and create features}
\item {Analyze and interpret the data and build-optimize the machine learning model}
      \end{cvitems}
    }
    
  \cventry
    {Freelance: Translate of autonomous routines built in R into Python. This includes} % Job title
    {TheMadFox - Colombia} % Organization
    {Remote Work} % Location
    {November 2020 - January 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
\item {Download and merge data using API.}
\item {Extrapolate data.}
\item {Create plot reports using Python - Plotly. }
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
  	{Data Analyst: Predict the dropout probability of a student using data from 1996 to 2020. Python and R. }% Job title 
    {Data Science for All (DS4A) - Remington University (Colombia)} % Organization
    {Remote Work} % Location
    {August 2020 - November 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
\item {Define and extract the dropout variable.}
\item {Clean and merge the data.}
\item {Define the Machine Learning Model (Random Forest).}
\item {Locate the data and the model into AWS (EC2).}
\item {Show and use the model in a Front End (Shiny - R).}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
  	{Science Programmer: Simulation of the efficiency $\epsilon$ of an HPGe detector using MonteCarlo (C++) and experimental data.}% Job title 
    {UNAM} % Organization
    {Mexico City, Mexico} % Location
    {January 2018 - June 2018} % Date(s)
    {}
\end{cventries}
